Impact of Water Conditions on Dissolved Oxygen Level

### 2024-04-19 paper/paper.qmd
Update paper.qmd

---
title: "Impact of Water Conditions on Dissolved Oxygen Level"
author: Wentao Sun
thanks: "Code and data are available at: https://github.com/TonySun1107/Water_Quality.git"
date: today
date-format: long
abstract: "This study conducts a thorough analysis of various water quality parameters including dissolved oxygen content, water temperature, salinity, and pH levels within aquatic environments. The research primarily investigates the impacts of temperature, salinity, and pH on the dissolved oxygen levels, key indicators of water quality, to discern patterns in environmental changes. Findings reveal that both temperature and salinity exert a negative influence on dissolved oxygen levels, with increases in these parameters correlating with reductions in oxygen availability. The comprehensive water quality analysis deployed in this research elucidates the intricate interactions among critical determinants of aquatic ecosystem health. Ultimately, this study enhances our understanding of how different environmental factors influence dissolved oxygen content, offering valuable insights for the management of aquatic ecosystems and advancing environmental sustainability efforts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

>>>>

---
title: "Impact of Water Conditions on Dissolved Oxygen Level"
subtitle: "An Analysis of U.S. Water Quality Data From 1989 to 2019"
author: Wentao Sun
thanks: "Code and data are available at: https://github.com/TonySun1107/Water_Quality.git"
date: today
date-format: long
abstract: "This study conducts a thorough analysis of various water quality parameters including dissolved oxygen content, water temperature, salinity, and pH levels within aquatic environments. The research primarily investigates the impacts of temperature, salinity, and pH on the dissolved oxygen levels, key indicators of water quality, to discern patterns in environmental changes. Findings reveal that both temperature and salinity exert a negative influence on dissolved oxygen levels, with increases in these parameters correlating with reductions in oxygen availability. The comprehensive water quality analysis deployed in this research elucidates the intricate interactions among critical determinants of aquatic ecosystem health. Ultimately, this study enhances our understanding of how different environmental factors influence dissolved oxygen content, offering valuable insights for the management of aquatic ecosystems and advancing environmental sustainability efforts."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
